Generating Simulated Data

### 2021-03-31 docs/SimData.Rmd
update sim data 1st of 4 survey growth pars

@@

@@

Need to fit growth and maturity parameters from Atlantis output for input into hydra. Fit growth using code below.

@@

  growthpars <- left_join(svexp3, vbout.2)

@@

  growthspp <- growthpars %>%
    filter(era==maxera) %>%
    select(species, psi, kappa, Linf, K) %>%
    t() %>%
    as.data.frame()

  write_csv(paste0(o.name,"growth_species_NOBA_",s,".csv"))
}
```

```{r lendat}
# rearrange into length bins and write length comp data csvs
#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

@@

@@

@@

```{r stomwt}

@@

We can get surface and bottom temp from Atlantis using the layers from each polygon, with layer 0 being the bottom and the maximum layer in the polygon being the surface (according to the [Atlantis wiki/Atlantis output files/Atlantis NetCDF structure](https://confluence.csiro.au/display/Atlantis/Atlantis+NetCDF+Structure). 
```{r surveytemp, eval=FALSE}

@@

## Generating a survey dataset

>>>>

#### Multispecies surplus production model (MSSPM)

@@

#### Length-structured multispecies model (Hydra)

@@

Need to fit growth and maturity parameters from Atlantis output for input into hydra. Fit growth using code below, based on the package FSA [@ogle-fsa-2021]. The package provides multiple ways to get starting values for the R `nls` function for fitting nonlinear models. It was necessary to try several different methods for starting values to get at least one von Bertalannfy growth parameter set for each species. A scratch code block shows some of the experiments to get the fitting working that resulted in the function to fit for all surveys.

@@

  growthpars <- left_join(svexp3, vbout.2) %>%
    mutate(growthType = 4) # use only vonB for now, can change later

@@

  growthspp <- growthpars %>%
    filter(era==maxera) %>%
    select(species, psi, kappa, Linf, K, growthType) %>%
    pivot_longer(psi:growthType, names_to = "par") %>%
    pivot_wider(names_from = species, 
                values_from = value) %>%
    ungroup() %>%
    select(-era) %>%
    remove_rownames %>% column_to_rownames(var="par") %>%
    write.csv(paste0(o.name,"growth_species_NOBA_era",maxera,"_",s,".csv"))
}

@@

This code block has experiments with different fits and different ways to splice the length at age data.

@@

```{r lendat, eval=FALSE}
# rearrange into length bins and write length comp data csvs
#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

@@

```{r stomwt, eval=FALSE}

@@

We can get surface and bottom temp from Atlantis using the layers from each polygon, with layer 0 being the bottom and the maximum layer in the polygon being the surface (according to the [Atlantis wiki/Atlantis output files/Atlantis NetCDF structure](https://confluence.csiro.au/display/Atlantis/Atlantis+NetCDF+Structure).

```{r surveytemp, eval=FALSE}

@@

#### Age structured multispecies statistical catch at age model (MSSCAA)

## References
